---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**NOTE: This is an incomplete package, more functions are to come.**

# lorR

<!-- badges: start -->
<!-- badges: end -->

The package can be used as handler for Legends of Runeterra API methods.

A series of utility functions to transform the outputs from the API are also included.

## Installation

You can install the development version of lorR from [GitHub](https://github.com/) with:

``` {r}
# install.packages("devtools")
devtools::install_github("MaouLegna/lorR")
```

## Setup

As an API key is necessary to work with the API methods, use the following to set up a Sys.setenv variable containing the key.

```{r}
if( Sys.getenv("LORAPI_key") != "" ) lorR::setAPIkey("RGAPI-01234567-abcd-8ef9-abcd-0123456789AB")
```

You can also put this in your .Rprofile for your project so you don't have to type it every time.

## Usage

The library provides a series of functions wraps the methods of the LoR API.

The outputs are returned either clean or json text format.

## Note

The package is still incomplete missing several fundamental functions.

Options beings considered:

* Working with setting that assume a Developer Key

* Working with multiple Developer Key


